Deep Neural Architectures for Discourse Segmentation in E-Mail Based Behavioral Interventions

### 2018-11-16 paper-amia-summit-2019/manuscript.tex
update response to reviewers

\subsection*{\textit{Evaluation metrics}}
We report standard metrics of precision, recall and F1-measure to evaluate the performance of the classifiers.\cite{aas1999text} Accuracy is not reported as a performance metric because it is highly sensitive to the prior class probabilities and does not fully describe the actual difficulty of the decision problem, when highly unbalanced datasets are involved. The results are reported based on 5 fold cross-validation and weighted macro-averaging over the folds. We also estimate the area under \hl{the precision-recall curve (AUPR) metric due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets.} \cite{davis2006relationship}

>>>>

\subsection*{\textit{Evaluation metrics}}
We report standard metrics of precision, recall and F1-measure to evaluate the performance of the classifiers.\cite{aas1999text} Accuracy is not reported as a performance metric because it is highly sensitive to the prior class probabilities and does not fully describe the actual difficulty of the decision problem, when highly unbalanced datasets are involved. The results are reported based on 5 fold cross-validation and weighted macro-averaging over the folds, \hl{in which each fold was used as a test set and remaining 4 folds was utilized as a train set}. We also estimate the area under \hl{the precision-recall curve (AUPR) metric due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets.} \cite{davis2006relationship}
